Replicator-mutator and noise-perturbed replicator dynamics

### 2014-10-20 paper/03_simulations.tex
plots reworked, almost all BW

  \caption{Examples for Nosofsky-similarity (non-normalized) and
    derived probability of state confusion (normalized) for
    $\card{\States} = 50$ and different
    values of $\impairment$.}
  \label{fig:NosofskySim}
\end{figure}

@@

  \includegraphics[width=\textwidth]{plots/confusion_sender.pdf}

  \includegraphics[width=\textwidth]{plots/confusion_receiver.pdf}

@@

  \includegraphics[width=0.9\textwidth]{plots/MeanMetrics.pdf}

@@

  \includegraphics[width=0.9\textwidth]{plots/CategoricalMeasures.pdf}

@@

    \includegraphics[width=\textwidth]{plots/WithinGroupMeasures.pdf}

>>>>

  \caption{Examples for Nosofsky-similarity (non-normalized) and
    derived probability of state confusion (normalized) for
    $\card{\States} = 50$ and different
    values of imprecision $\impairment$.}
  \label{fig:NosofskySim}
\end{figure}

@@

  \includegraphics[width=0.9\textwidth]{plots/confusion_sender.pdf}

  \includegraphics[width=0.9\textwidth]{plots/confusion_receiver.pdf}

@@

  \includegraphics[width=\textwidth]{plots/MeanMetrics.pdf}

@@

  \includegraphics[width=0.8\textwidth]{plots/CategoricalMeasures.pdf}

@@

    \includegraphics[width=0.8\textwidth]{plots/WithinGroupMeasures.pdf}

### 2014-10-20 snippets/Nosofsky_similarity.Rmd
plots reworked, almost all BW

```{r warning=FALSE, echo=FALSE, message=FALSE}
library(ggplot2)
library(reshape2)
```

@@

simDF = data.frame(distance = rep(states,2*length(alphas)),
                   alpha = factor(rep(rep(alphas, each=ns),2)),
                   normalized = factor(rep(c("non-normalized", "normalized"),each=ns*length(alphas))),
                   similarity = c(as.vector(t(out)),as.vector(t(outNorm)))  )

p = ggplot(simDF, aes(x = distance, y = similarity, color=alpha)) + geom_point() +
  geom_line() + facet_grid(normalized~. , scales = "free")

@@

pdf('paper/plots/NosofskySim.pdf', width=7, height=4)
show(p)
dev.off()
```

>>>>

```{r warning=FALSE, echo=FALSE, message=FALSE}
library(ggplot2)
library(reshape2)
theme_set(theme_bw())
```

@@

simDF = data.frame(distance = rep(states,2*length(alphas)),
                   alpha_i = factor(rep(rep(alphas, each=ns),2)),
                   normalized = factor(rep(c("Nosofsky similarity", "confusion probability"),each=ns*length(alphas)),
                                       levels = c("Nosofsky similarity", "confusion probability")),
                   similarity = c(as.vector(t(out)),as.vector(t(outNorm)))  )

p = ggplot(simDF, aes(x = distance, y = similarity, shape = alpha_i))+
  geom_line(color='grey')  + geom_point()  + 
  facet_grid(normalized~. , scales = "free") + ylab("") + 
  xlab("distance in physical space") +
  scale_shape_discrete(name="imprecision")

@@

ggsave(p, file="paper/plots/NosofskySim.pdf", width=7, height=4)

```

### 2014-10-20 snippets/data_exploration/data_exploration_tmp.Rmd
plots reworked, almost all BW

pd <- position_dodge(.01)
sp = ggplot(dsub, aes(x=Impairment, y=value, colour=Number.of.states)) + 
     geom_point(position = pd) +
     geom_errorbar(aes(ymin=value-ci, ymax=value+ci), width=0, position=pd) +
     geom_line(position=pd) + xlab("imprecision")

sp = sp + facet_grid(variable ~ Tolerance, scales="free")

show(sp)

pdf("~/Desktop/data/svn/vagueness-games/paper/plots/MeanMetrics.pdf", width=8, height = 6)
show(sp)
dev.off()

@@

sp = ggplot(dms, aes(x=factor(Impairment), y = value)) 
sp = sp + geom_bar(aes(fill = variable), color = "black", stat="identity", position= position_dodge(0.4), width = 0.35)
sp = sp + facet_grid(Number.of.states ~ Tolerance, scales="free") + ylab("proportion") + xlab("imprecision")

show(sp)

pdf("~/Desktop/data/svn/vagueness-games/paper/plots/CategoricalMeasures.pdf", width=8, height = 5)
show(sp)
dev.off()

>>>>

myLabeller <- function(var, value){
    value <- as.character(value)
    if (var=="variable") { 
        value[value=="Speaker.entropy"] <- "entropy sen"
        value[value=="Hearer.entropy"] <- "entropy rec"
        value[value=="Speaker.informativity"] <- "informativity"
        value[value=="Speaker.Voronoiness"] <- "Voronoiness sen"
        value[value=="Hearer.Voronoiness"] <- "Voronoiness rec"
        value[value=="Expected.utility"] <- "expected utility"
    }
    return(value)
}

pd <- position_dodge(.01)
mysize = 1.65
sp = ggplot(dsub, aes(x=Impairment, y=value, color = Number.of.states, shape=Number.of.states, linetype=Number.of.states)) + 
    geom_line(color="gray", position = pd) + xlab("imprecision") +
     geom_point(position = pd, size = mysize) +
     geom_errorbar(aes(ymin=value-ci, ymax=value+ci), width=0, position=pd) +
    scale_shape_discrete(name = "# states") +
    scale_linetype_discrete(name = "# states") +
    scale_color_discrete(name = "# states")

sp = sp + facet_grid(variable ~ Tolerance, scales="free", labeller=myLabeller)

sp + facet_grid(. ~ sex, labeller=mf_labeller)
show(sp)

ggsave(sp, file = "paper/plots/MeanMetrics.pdf", width=8, height = 8)

@@

pd <- position_dodge(.05)
sp = ggplot(dms, aes(x=factor(Impairment), y = value, group = variable, shape = variable, linetype = variable)) 
sp = sp + geom_line(position = pd, color = "grey") + geom_point(position = pd)
sp = sp + facet_grid(Number.of.states ~ Tolerance, scales="free") + ylab("proportion") + xlab("imprecision") +
  scale_shape_discrete(name = "property") +
  scale_linetype_discrete(name = "property")
show(sp)
ggsave(sp, file = "paper/plots/CategoricalMeasures.pdf", width=8, height = 5)

### 2014-10-20 snippets/iteration_diffusion.Rmd
plots reworked, almost all BW

```{r warning=FALSE, echo=FALSE, message=FALSE}
library(MCMCpack) # for Dirichlet distribution
library(ggplot2)
library(reshape2)
# source('~/Desktop/data/svn/programming/R/fuzzy-action/dev.r')
```

@@

plotSender = function(sen){
  senDF = melt(sen,varnames = c("state.index","message"), value.name = "probability")
  senDF$states = states[senDF[,1]]
  senDF$message = factor(senDF$message)
  ggplot(senDF, aes(x = states, y=probability, color=message)) + geom_point() + geom_line()
}

>>>>

```{r warning=FALSE, echo=FALSE, message=FALSE}
library(MCMCpack) # for Dirichlet distribution
library(ggplot2)
library(reshape2)
theme_set(theme_bw())
greyPalette = c("#999999", "#222222", "#999999", "#000000", "#999999", "#000000", "#999999", "#000000")
# source('~/Desktop/data/svn/programming/R/fuzzy-action/dev.r')
```

@@

ns = 50
nm = 2
rounds = c(1,2,10,50,1000)
alphas = c(0.01,0.05,0.1,0.3)

plotSender = function(ns,nm,alphas,rounds){
  sen = rdirichlet(ns,rep(1,nm))
  senDF = data.frame(state = 0,
                     message = 0,
                     round = 0,
                     alpha = 0,
                     probability = 0)

  for (alpha in alphas){
    C = get.confusion.matrix(get.states(ns),alpha)
    newDF = data.frame(state = rep(get.states(ns),nm),
                       message = rep(1:2,each=ns),
                       round = rep(0,ns*nm),
                       alpha = rep(alpha,ns*nm),
                       probability = as.vector(sen))
    for (r in rounds){
      newC = power(C,r)
      newSen = get.nbr(sen,newC)
      newDF2 = data.frame(state = rep(get.states(ns),nm),
                          message = rep(1:2,each=ns),
                          round = rep(r,ns*nm),
                          alpha = rep(alpha,ns*nm),
                          probability = as.vector(newSen))
      newDF = rbind(newDF,newDF2)                   
      }
    senDF = rbind(senDF,newDF)
  }
  senDF = senDF[-1,]
  senDF$message = factor(senDF$message)
  senDF$alpha = factor(senDF$alpha)
  p = ggplot(senDF,aes(x = state, y = probability, color = message)) + 
      geom_line() + facet_grid(alpha~round) +
                                          scale_colour_manual(values=greyPalette) +
      ggtitle("sender") +
      scale_x_continuous(breaks=seq(0,1,1/2)) +
      theme(axis.text.x  = element_text(angle=90, vjust=0.5)) + 
      scale_y_continuous(breaks=seq(0,1,1/2))

  return(p)
}

plotReceiver = function(ns,nm,alphas,rounds){
  rec = rdirichlet(nm,rep(1,ns))
  recDF = data.frame(state = 0,
                     message = 0,
                     round = 0,
                     alpha = 0,
                     probability = 0)

  for (alpha in alphas){
    C = get.confusion.matrix(get.states(ns),alpha)
    newDF = data.frame(state = rep(get.states(ns),nm),
                       message = rep(1:2,each=ns),
                       round = rep(0,ns*nm),
                       alpha = rep(alpha,ns*nm),
                       probability = as.vector(t(rec)))
    for (r in rounds){
      newC = power(C,r)
      newRec = get.nbr(rec,newC)
      newDF2 = data.frame(state = rep(get.states(ns),nm),
                          message = rep(1:2,each=ns),
                          round = rep(r,ns*nm),
                          alpha = rep(alpha,ns*nm),
                          probability = as.vector(t(newRec)))
      newDF = rbind(newDF,newDF2)                   
      }
    recDF = rbind(recDF,newDF)
  }
  recDF = recDF[-1,]
  recDF$message = factor(recDF$message)
  recDF$alpha = factor(recDF$alpha)
  p = ggplot(recDF,aes(x = state, y = probability, color = message)) + 
       geom_line() + facet_grid(alpha~round) +
                                          scale_colour_manual(values=greyPalette) +
      scale_x_continuous(breaks=seq(0,1,1/2)) +
      ggtitle("receiver") +
      theme(axis.text.x  = element_text(angle=90, vjust=0.5)) + 
      scale_y_continuous(breaks=seq(0,round(max(recDF$probability),2),round(max(recDF$probability),2)/2))
  return(p)
}

pSen = plotSender(ns,nm,alphas,rounds)
pRec = plotReceiver(ns,nm,alphas,rounds)
show(pSen)
show(pRec)

ggsave(pSen, file = "paper/plots/confusion_sender.pdf", width = 7, height = 4)

ggsave(pRec, file = "paper/plots/confusion_receiver.pdf", width = 7, height = 4)
